Model Search in Relational Domains

### 2016-10-23 experiments.tex
deduction text
Spelling

We verified a total of 66 ANSI-C benchmarks, which are derived from (a)~the
bit-vector regression category in SV-COMP'16, (b)~bit-precise and
cycle-accurate software models of hardware circuits automatically generated
using v2c~\cite{mtk2016}, (c)~controller code generated from Simulink
(d)~several hand-crafted benchmarks for equivalence checking and bounded
loop analysis.  All bounded loops are completely unrolled before analysis. 
We compare our tool with a state-of-the-art SAT-based bounded model checker
CBMC (version 5.5)~\cite{cbmc} and a commercial static analysis tool, 
Astr{\'e}e (version 14.10). 
CBMC uses MiniSAT~2.2.1 in the backend.  Astr{\'e}e uses a 
range of abstract domains, which includes interval, 
bit-field, congruence, trace partitioning and relational domains
(octagons, polyhedra, zones, equalities, filter).  ACDCL is instantiated
with a product domain of booleans and template polyhedra.  We use the
interval and octagon templates for our experiments.  ACDCL is configured
with a heuristic choice of decision (ordered, random, berkmin), propagation
(forward and multi-way) and conflict-analysis (learning UIP, DPLL-style). 
The timeout for our experiments is set to one hour.
%
\Omit {
To enable precise analysis using Astr{\'e}e, all our benchmarks are 
manually instrumented with partition directives which provides external 
hint to the tool to guide the trace partitioning heuristics.  Usually, 
such high-precision is not needed for static analysis, since it makes 
the analysis very expensive.  Without trace partitioning, the 
analysis using Astr{\'e}e shows high degree of imprecision. 
}

\paragraph {\textbf{Precision and Efficiency of Analysis}}
%
Figure~\ref{fig:results} presents a comparison of the analyses using CBMC
and ACDCL.  Figure~\ref{fig:results}(a) clearly shows that the SAT solver
made significantly more decisions compared to ACDCL for all the benchmarks. 
The points on the extreme right below the diagonal in
Figure~\ref{fig:results}(b) show that the number of propagations in the SAT
solver is maximal for the benchmarks that exhibit relational behavior. 
Cumulative statistics corresponding to each phase of the algorithm for all
66 benchmarks is given in Table~\ref{result}.  We observe a reduction of at
least two orders of magnitude in the number of decisions, propagations and
conflicts compared to analyis using CBMC.

\begin{table}[t]
\begin{center}
{
\begin{tabular}{l|r|r|r|r|r}
\hline
Solver & Decisions & propagations & conflict & conflict literals & restarts \\ \hline
MiniSat & 27917 & 304031 & 3949 & 33646 & 64 \\ \hline
ACDCL (Product Domain) & 161 & 3130 & 10 & 5 & 0 \\ \hline  
\end{tabular}
}
\end{center}
\caption{Solver statistics}
\label{result}
\end{table}

Out of 66 benchmarks, CBMC with MiniSAT backend could only prove 16
benchmarks without any restarts.  The solver is restarted in 50 cases to
avoid spending too much time in ``hopeless'' branches.  By contrast, the
analysis using ACDCL solved all 66 benchmarks without any restarts.  This is
attributed to our decision heuristics, which exploit the high-level
structure of the program combined with the stronger deduction and clause
learning mechanisms aided by the richer abstract domains.  On the other
hand, Ast{\'e}e is often faster than ACDCL, but the analysis using
Astr{\'e}e shows a high degree of imprecision.  Astr{\'e}e reported 15 false
alarms for the 41 safe benchmarks.

@@

\paragraph {\textbf{Decision Heuristics}}
%
Figure~\ref{prop-dec}(b) presents a visualization of the performance of
different decision heuristics in ACDCL.  Note that the runtimes for all
decision heuristics are obtained with multi-way propagtion strategy.  The
runtimes are very close, but we observe some key characteristics of these
heuristics.  Berkmin heuristic performs consistently well for most safe
benchmarks and all bit-vector category benchmarks.  Whereas, the ordered
heuristic performs better for programs with conditional branches since it
prioritises decisions on meet irreducibles that appear in conditional
branches over meet irreducibles that involve numerical variables.  Whereas,
the runtimes for random heuristic is marginally higher than the other two. 
This suggest that domain-specific decision heuristics are important for
ACDCL.

\Omit{
Whereas activity-based heuristics such as Berkmin heuristic which 
works well in propositional cases performs best for benchmarks 
that encountered the maximum number of conflicts to prove safety, 
thus allowing the heuristics to choose the decison variable among the set of learnt clauses.   
}

\paragraph {\textbf{Learning}}
%
Learning has a significant influence on the runtime of ACDCL.  We compare
the UIP-based learning technique with an analysis that performs
chronoligical backtracking without learning.  The effect of UIP computation
allows ACDCL to backtrack non-chronologically and guide the model search
with a learnt transformer.  However, the DPLL-style analysis exhibits
case-enumeration behavior and could not finish within the time bound for
20\% of our benchmarks.

>>>>

We verified a total of 66 ANSI-C benchmarks, which are derived from (a)~the
bit-vector regression category in SV-COMP'16, (b)~bit-precise and
cycle-accurate software models of hardware circuits automatically generated
using v2c~\cite{mtk2016}, (c)~controller code generated from Simulink
(d)~several hand-crafted benchmarks for equivalence checking and bounded
loop analysis.  All bounded loops are completely unrolled before analysis. 
We compare our tool with a state-of-the-art SAT-based bounded model checker
CBMC (version 5.5)~\cite{cbmc} and a commercial static analysis tool, 
Astr{\'e}e (version 14.10). 
CBMC uses MiniSAT~2.2.1 in the backend.  Astr{\'e}e uses a 
range of abstract domains, which includes interval, 
bit-field, congruence, trace partitioning and relational domains
(octagons, polyhedra, zones, equalities, filter).  ACDCL is instantiated
with a product domain of Booleans and template polyhedra.  We use the
interval and octagon templates for our experiments.  ACDCL is configured
with a heuristic choice of decision (ordered, random, berkmin), propagation
(forward and multi-way) and conflict-analysis (learning UIP, DPLL-style). 
The timeout for our experiments is set to one hour.
%
\Omit {
To enable precise analysis using Astr{\'e}e, all our benchmarks are 
manually instrumented with partition directives which provides external 
hint to the tool to guide the trace partitioning heuristics.  Usually, 
such high-precision is not needed for static analysis, since it makes 
the analysis very expensive.  Without trace partitioning, the 
analysis using Astr{\'e}e shows high degree of imprecision. 
}

\paragraph {\textbf{Precision and Efficiency of Analysis}}
%
Figure~\ref{fig:results} presents a comparison of the analyses using CBMC
and ACDCL.  Figure~\ref{fig:results}(a) clearly shows that the SAT solver
made significantly more decisions compared to ACDCL for all the benchmarks. 
The points on the extreme right below the diagonal in
Figure~\ref{fig:results}(b) show that the number of propagations in the SAT
solver is maximal for the benchmarks that exhibit relational behaviour. 
Cumulative statistics corresponding to each phase of the algorithm for all
66 benchmarks is given in Table~\ref{result}.  We observe a reduction of at
least two orders of magnitude in the number of decisions, propagations and
conflicts compared to analysis using CBMC.

\begin{table}[t]
\begin{center}
{
\begin{tabular}{l|r|r|r|r|r}
\hline
Solver & Decisions & propagations & conflict & conflict literals & restarts \\ \hline
MiniSat & 27917 & 304031 & 3949 & 33646 & 64 \\ \hline
ACDCL (Product Domain) & 161 & 3130 & 10 & 5 & 0 \\ \hline  
\end{tabular}
}
\end{center}
\caption{Solver statistics}
\label{result}
\vspace*{-3ex} %BAD TRICK
\end{table}

Out of 66 benchmarks, CBMC with MiniSat backend could only prove 16
benchmarks without any restarts.  The solver is restarted in 50 cases to
avoid spending too much time in ``hopeless'' branches.  By contrast, the
analysis using ACDCL solved all 66 benchmarks without any restarts.  This is
attributed to our decision heuristics, which exploit the high-level
structure of the program combined with the stronger deduction and clause
learning mechanisms aided by the richer abstract domains.  On the other
hand, Ast{\'e}e is often faster than ACDCL, but the analysis using
Astr{\'e}e shows a high degree of imprecision.  Astr{\'e}e reported 15 false
alarms for the 41 safe benchmarks.

@@

\paragraph {\textbf{Decision Heuristics}}
%
Figure~\ref{prop-dec}(b) presents a visualisation of the performance of
different decision heuristics in ACDCL.  Note that the runtimes for all
decision heuristics are obtained with multi-way propagation strategy.  The
runtimes are very close, but we observe some key characteristics of these
heuristics.  Berkmin heuristic performs consistently well for most safe
benchmarks and all bit-vector category benchmarks.  Whereas, the ordered
heuristic performs better for programs with conditional branches since it
prioritises decisions on meet irreducibles that appear in conditional
branches over meet irreducibles that involve numerical variables.  Whereas,
the runtimes for random heuristic is marginally higher than the other two. 
This suggest that domain-specific decision heuristics are important for
ACDCL.

\Omit{
Whereas activity-based heuristics such as Berkmin heuristic which 
works well in propositional cases performs best for benchmarks 
that encountered the maximum number of conflicts to prove safety, 
thus allowing the heuristics to choose the decision variable among the set of learnt clauses.   
}

\paragraph {\textbf{Learning}}
%
Learning has a significant influence on the runtime of ACDCL.  We compare
the UIP-based learning technique with an analysis that performs DPLL-style 
analysis.
%chronoligical backtracking without learning.  
The effect of UIP computation allows ACDCL to backtrack non-chronologically 
and guide the model search with a learnt transformer.  However, the DPLL-style 
analysis exhibits case-enumeration behaviour and could not finish within the 
time bound for 20\% of our benchmarks.
